\documentclass{harnon-cv}


\usepackage{verbatim}
\usepackage{numprint}

% personal details
\yourname{Vincent Hong Cai}
\yournumber{(973)710-5153}
\youraddress{228 Stewart Ave\\Kearny, NJ 07032}
\youremail{vincent.hong.cai@gmail.com}

%personal statement
\recenthistory{Oracle Certified Professional, Java SE 7 Programmer with 4-year work experience.}

\begin{document}

\maketitle

\begin{comment}
% Objective
\addheadertext{Objective}
A challenging position in the field of Software Engineering.
\end{comment}

% Technical Skills
\addheadertext{Technical Skills}
\begin{itemize}\itemsep1pt
\item Proficient in developing enterprise applications using core Java including JVM, multi-threading, collections, garbage collection, reflection, Java internationalization, file I/O, exception handling.
\item Expertise in various open source frameworks and tools such as Maven, Gradle, Struts, Spring, Hibernate, Log4j, JUnit and Mockito.
\item Working experience with various database systems including Oracle and MySQL. Thorough knowledge in PL/SQL statements, writing queries using SQL and formatting results.
\item Extensive knowledge and hands on experience with J2EE technologies developing web application using JDBC, Servlets, JSP, JSTL, Java Beans, JMS, HTML, CSS, JavaScript, Ajax, DOM Parser, XML.
\item Extensive knowledge with developing SOAP and RESTful web service using JAX-WS API, JAX-RS API, XML and JSON.
\item Efficient use of various design patterns in development such as Singleton, Factory, Proxy, Stratergy, Flyweight, Front Controller, Template Method, Session Facade, Service Locator and DAO.
\item Experience in various version control systems, including SVN and Git.
\item Good understanding and hands on work experience in both Agile and Waterfall methodologies. Involved in all phases of software development life cycle (SDLC) process including requirement analysis, specification, implementation, testing, debugging, product maintenance, documentation and process management.
\item Excellent troubleshooting skills and proactive problem solving approach with excellent leadership, inter-personal, time management skills and strong analytical presentation, ability to work independently and active team player with proven work ethics.
\end{itemize}\par


% Experience
\addheadertext{Work Experience}
\starttimeline
\timelineitem{Oct. 2011 - Now} {
    \addsubheader{Software Engineer, Advanced Power Technology, Randolph, NJ}
    \addtimelinebullet{Built a web application for Eclipse Power Transformer Protective Systems that deals with the day-to-day operation of multiple power transformers in different remote locations. }
    \addtimelinebullet{Used Apache Tomcat for application server to implement the J2EE Platform, create applications and integrate applications with other applications.}
    \addtimelinebullet{Implemented the business logic that allowed users to process data, perform calculations, sort data by project and date, and generate reports over a secured connection with data security.}
    \addtimelinebullet{Developed the email alert service that allowed users to receive notification when emergency happens. }
    \addtimelinebullet{Integrated user interface layer with persistence layer through Spring 3.1 and Hibernate 3.5.}
    \addtimelinebullet{Handled Java Multi-Threading part in back-end component, one thread will be running for each user, which serves that user.}
    \addtimelinebullet{Dealt with Hibernate 3.5 ORM framework for persistence management.}
}
\stoptimeline\par

% Patent
\addheadertext{Patent}
\starttimeline
\timelineitem{April 28, 2015}{
    \addsubheader{Method and apparatus for protecting power transformers from large electro-magnetic disturbances}
    \addtimelinebullet{Inventors: Gary R. Hoffman, Edward S. Kwon, Hong Cai}
    \addtimelinebullet{Patent status: Granted | Patent number: 9,018,962}
}
\stoptimeline

% Education
\addheadertext{Education \& Certification}
\starttimeline
\timelineitem{Aug. 2015}{
    \addsubheader{Oracle Certified Professional, Java SE 7 Programmer}
    \addtimelinebullet{License Number: 236752924}
    \addtimelinebullet{Score: 80\%}
}
\timelinespacer
\timelineitem{May. 2011}{
    \addsubheader{M.S. Computer Engineering}
    \addtimelinebullet{New Jersey Institute of Technology, Newark, NJ }
    \addtimelinebullet{GPA: 3.5/4.0}
}
\timelinespacer
\timelineitem{Jun. 2009}{
    \addsubheader{B.S. Electrical Engineering}
    \addtimelinebullet{Changshu Institute of Technology, Suzhou, Jiangsu, China}
    \addtimelinebullet{GPA: 3.2/4.0}
}
\stoptimeline

% School Java Projects
\addheadertext{School Projects}
\starttimeline
\timelineitem{April. 2011}{
    \addsubheader{Sub Killer Game}
    \addtimelinebullet{Developed the on-line sub killer game for multiple users using Java Applet connecting with Oracle Database.}
    \addtimelinebullet{The user moved the boat with the left and right arrow keys and dropped bomb with the down arrow key. The user could change the speed level of submarine to make game more difficult. The database stored the hit rate of current user.}

}
\timelinespacer
\timelineitem{Nov. 2010}{
    \addsubheader{Website Poster}
    \addtimelinebullet{Developed the on-line HTML file creating tool: the website poster.}
    \addtimelinebullet{The function of the tool was to generate HTML tags automatically such that the users only needed to focus on the content of the web pages. This tool saved time for web page development. It was also able to display the appearance of the web page at the same time.}
 }

\timelinespacer
\timelineitem{April. 2010}{
    \addsubheader{On-line Exam System}
    \addtimelinebullet{The on-line php oracle exam system has 3 levels of access control including student, professor and administrator.}
\addtimelinebullet{The administrator could create profile for student and professor. The professor could design the exam. The student could register a course and take exam. Exam could be scored automatically.}
}
\stoptimeline

\end{document}
